A thesis draft

### 2018-11-28 res/sections/25-TestsResponsiveness.tex
Remove duplicated part

\paragraph*{Considerations on container start-up in Kubernetes}
Regarding the start-up times in Kubernetes is possible to denote a considerable
difference between the deployment of a SFC with only one element
(\textit{de facto} only one container) with a single container directly launched
on Docker. The difference, of many seconds, can be easily explained: the
creation of a Docker container, \textit{per se}, is quite fast compared to the
scheduling job the Kubernetes cluster has to do before launching the pod. A
Kubernetes deployment is indeed a rather complex operation than launching a
simple container. When a new deployment is launched on Kubernetes, the operation
initiate with the scheduling of a Pod. A Pod can have several lifecycle
states~\cite{kubePodLifecycle}:
\begin{description}
\item[pending:] The Pod has been accepted by the Kubernetes system, but one or
  more of the Container images has not been created. This includes time before
  being scheduled as well as time spent downloading images over the network,
  which could take a while;
\item[running:] The Pod has been bound to a node, and all of the Containers have
  been created. At least one Container is still running, or is in the process of
  starting or restarting;
\item[succeeded:] All Containers in the Pod have terminated in success, and will
  not be restarted;
\item[failed:] All Containers in the Pod have terminated, and at least one
  Container has terminated in failure. That is, the Container either exited with
  non-zero status or was terminated by the system;
\item[unknown:] For some reason the state of the Pod could not be obtained,
  typically due to an error in communicating with the host of the Pod.
\end{description}

On top of that, different conditions can affect a Pod:
\begin{itemize}
\item \verb!PodScheduled!: the Pod has been scheduled to a node;
\item \verb!Ready!: the Pod is able to serve requests and should be added to the
  load balancing pools of all matching Services;
\item \verb!Initialized!: all ``Init Containers'' have started successfully;
\item \verb!Unschedulable!: the scheduler cannot schedule the Pod right now, for
  example due to lacking of resources or other constraints.
\end{itemize}

>>>>

\paragraph*{Considerations on container start-up in Kubernetes}
Regarding the start-up times in Kubernetes is possible to denote a considerable
difference between the deployment of a SFC with only one element
(\textit{de facto} only one container) with a single container directly launched
on Docker. The difference, of many seconds, can be easily explained: the
creation of a Docker container, \textit{per se}, is quite fast compared to the
scheduling job the Kubernetes cluster has to do before launching the pod. A
Kubernetes deployment is indeed a rather complex operation than launching a
simple container. When a new deployment is launched on Kubernetes, the operation
initiate with the scheduling of a Pod. A Pod can have several lifecycle
states, that are explained in~\ref{pod}.
